---
title: "Project 3: Visualization Presentation"
subtitle: "Top 2000 Anime Plots"
author: "Macy Routh"
date: '2022-05-04'
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

I used the tidyverse and ggplot2 packages to plot my visualizations.

```{r, echo = TRUE}
library(tidyverse)
library(ggplot2)
```

## DataSet Used

I used the MyAnimeList Top 2000 Anime dataset found on Kaggle.

This dataset compiles the top 2000 anime from the website [MyAnimeList] (https://myanimelist.net/).

## Variables in the Dataset

11 variables of information are provided:

> - 'Name': the name of the Anime
> - 'Type': the entry's type (TV, Movie, or Music)
> - 'Score': the score of the anime based on 4 characteristics produced by MyAnimeList
> - 'Rank': the rank of the anime based on it's score
> - 'Popularity Rank': the rank of the anime based on it's popularity

## Variables in the Dataset

> - 'Air Date': the time frame of which the anime aired
> - 'Studio': the studio that worked on the anime
> - 'Number of Episodes': the number of episodes in each anime
> - 'Genre': the genre of the anime
> - 'Themes': the theme of the anime
> - 'Demographics': the anime's target audience

```{r}
data <- read.csv("mal_top2000_anime.csv")
```

## Scatterplot of Score and Popularity Rank

```{r}
library(ggplot2)
anime_data <- read_csv("mal_top2000_anime.csv")
anime_data %>%
ggplot(anime_data, mapping = aes(x = `Popularity Rank`, y = Score)) + geom_point(color = "navyblue", size = 0.5, width = 0.5) + labs(title = "Correlation between Score and Popularity of Anime")
```

## Scatterplot of Number of Episodes and Popularity Rank

```{r}
library(ggplot2)
anime_data <- read_csv("mal_top2000_anime.csv")
anime_data %>%
ggplot(anime_data, mapping = aes(x = `Num. of episodes`, y = `Popularity Rank`)) + geom_point(color = "navyblue", size = 0.5, width = 0.5, title = "Correlation between Score and Popularity") + xlim(0, 100) + xlab(label = "Number of episoides") + labs(title = "Anime Popularity Rank by Number of Episodes")
```

## Boxplot of Score Rank by Type of Anime

```{r}
anime_data <- read_csv("mal_top2000_anime.csv")
factor_data <- factor(anime_data$Type)
new_order_data <- factor(factor_data, levels = c("Movie", "TV", "Special", "ONA", "OVA", "Music"))
?geom_boxplot()
anime_data %>%
  ggplot(anime_data, mapping = aes(x = new_order_data, y = `Score Rank`)) + geom_boxplot(fill = c("green1", "yellow1", "orange1", "red1", "purple1", "blue1")) + xlab(label = "Type of Anime") + labs(title = "Score Rank by Type of Anime")
```